Project, Virtual Reality\\Group 8

### 2013-05-21 Developer/VR/paper.tex
Submitted VR paper

\title{Project, Virtual Reality}
\author{Stefan Eilemann, Benjamin Long}

@@

\fix{screenshots}

@@

\fix{Physics:}

@@

@@

This project contributed new functionality into an existing open source
project. While this added requirements to the project, this work immediately
benefits the existing users. Furthermore, building unto an existing framework
also facilitates the implementation due to the reuse of existing infrastructure
and functionality, e.g., the already-build rendering application. The resulting
demo is also rich in features and can easily be deployed on virtually all types
of display systems.

Due to the previous knowledge with Equalizer, the integration of the spacemouse
and OpenCV was relatively straightforward. The correct design of integrating
camera-based tracking took some time to figure o out. At first, a synchronous
approach polling the camera each frame was used, where the actual detection was
used to another thread. This proved too complex and hard to integrate cleanly
into the existing design, which was finally solved by an asynchronous approach
injecting events into the already distributed event processing. The chosen
design is simple in its implementation and robust in execution.

\fix{Share your experience. What were the difficulties? What you liked and/or
  disliked while developing this project? What you have learned?}

>>>>

\title{Project, Virtual Reality\\Group 8}
\author{Stefan Eilemann, Benjamin Long}

@@

@@

%\fix{Physics:}

@@

Since our project is embedded in a larger software, building it may be a bit
more complex. The build and functionality has been test on Mac OS X 10.8 using
the command line XCode utilities and MacPorts. Equalizer and all its
dependencies is build using the Buildyard multi-project CMake build tool, which
will download, configure, compile and install all projects in the correct
order. The only other dependencies to be installed are MacPort and the official
Mac OS X drivers for the SpaceMouse, and then the example can be build as
follows:

\begin{lstlisting}
sudo port install bullet +universal
sudo port install boost +universal
sudo port install opencv +universal
sudo port install cmake
cd Buildyard
make Equalizer
\end{lstlisting}

Afterwards everything is installed in \textsf{Build}, and the \textsf{eqPly}
example application can be launched:

\begin{lstlisting}
./Build/Equalizer/bin/eqPly.app/Contents/MacOS/eqPly
\end{lstlisting}

@@

This project contributed new functionality into an existing open source
project. While this added additional requirements to the project, this work
immediately benefits the existing users of the Equalizer parallel rendering
framework. Furthermore, building unto an existing framework also facilitates the
implementation due to the reuse of existing infrastructure and functionality,
e.g., the already-build rendering application. The resulting demo is rich in
features and can easily be deployed on virtually all types of display systems.

\begin{wrapfigure}{r}{.312\textwidth}
  \includegraphics[width=.312\textwidth]{screenshot}
  {\caption{\label{fScreenshot}eqPly running in a five-sided cave emulation}}
\end{wrapfigure}
Due to the previous knowledge with Equalizer, the integration of the spacemouse
and OpenCV was relatively straightforward. The correct design of integrating
camera-based tracking took some time to figure o out. At first, a synchronous
approach polling the camera each frame was used, where the actual detection was
used to another thread. This proved too complex and hard to integrate cleanly
into the existing design, which was finally solved by an asynchronous approach
injecting events into the already distributed event processing. The chosen
design is simple in its implementation and robust in execution.
